### 2023-10-10 main.tex
l
ss

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. By varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Thus, the coefficient of the above formula can be written as

@@

\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}. Indeed, by adapting \eqref{PsiI-N2} we obtain 

@@

that is exactly equation (4.26) of \cite{frassek2020eigenstates}.

@@

We give some examples of correlations applying formula \eqref{exactCorrelations}.

@@

	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})

@@

\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}

@@

	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})

@@

	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})

@@

		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
\paragraph{Three points correlations}

@@

    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})

@@

        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})

@@

	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 

>>>>

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. By varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Thus, the coefficient of the above formula can be written as

@@

\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}. Indeed, by adapting \eqref{PsiI-N2} we obtain 

@@

@@

We give examples  of correlations for up to three points applying formula \eqref{exactCorrelations}.

@@

	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})\dt

@@

\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}\dt

@@

	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})\dt

@@

	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\dt

@@

		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)\dt
\paragraph{Three-point correlations}

@@

    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})\dt

@@

        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt

@@

	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}. 
